Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas

### 2021-04-14 analysis/paper/paper.Rmd
EXPLORED CHANGES TO CALENDAR PLOT
explored adding day of week labels back. left as is for now.

```{r seal-hours-calendar, fig.height = 4.75, include=TRUE, fig.id = "dataCal", fig.cap="Distribution of haul-out behavior data from 1 March to 15 July for each species. The higher density of data from May and June coincides with peak molting when seals (and their attached bio-loggers) are more likely hauled out. Additionally, a majority of deployments started in April and May. Data were collated across all years between 2005 and 2020."}
ggplot(data = seal_hours_tbl) + 
  geom_point(aes(x = wkofyr, y = dayofwk, color = n, size = n), stroke = 0, shape = 15) +
  scale_size(range = c(1,4.35)) +
  scale_color_gradient(low = "#6baed6", high = "#08306b") +
  scale_x_continuous(breaks = c(13,18,23,27),
                     labels = c("April", "May", "June", "July")) +
  guides(color = "none",
        size = guide_legend(override.aes = list(color = "#2171b5"),
                            title.position = "bottom", title.hjust = 0.5)
        ) +
  facet_grid(species ~ .) + 
  theme(axis.text.y = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom") +
  labs(x = "", y = "day of week", color = "seal-hours",
       size = "seal hours of bio-logger data") +
  ggtitle("Haul-out behavior data is concentrated in the months of May and June",
          subtitle = "data presented in seal-hours collated across years (2005-2020)")
```

>>>>

```{r seal-hours-calendar, fig.height = 4.75, include=TRUE, fig.id = "dataCal", fig.cap="Distribution of haul-out behavior data from 1 March to 15 July for each species. The higher density of data from May and June coincides with peak molting when seals (and their attached bio-loggers) are more likely hauled out. Additionally, a majority of deployments started in April and May. Data were collated across all years between 2005 and 2020."}
ggplot(data = seal_hours_tbl) + 
  geom_point(aes(x = wkofyr, y = dayofwk, color = n, size = n), stroke = 0, shape = 15) +
  scale_size(range = c(1,4.35)) +
  scale_color_gradient(low = "#6baed6", high = "#08306b") +
  scale_x_continuous(breaks = c(13,18,23,27),
                     labels = c("April", "May", "June", "July")) +
  #scale_y_discrete(labels = c("Sat","","","Wed","","","Sun"))+
  guides(color = "none",
        size = guide_legend(override.aes = list(color = "#2171b5"),
                            title.position = "bottom", title.hjust = 0.5)
        ) +
  facet_grid(species ~ .) + 
  theme(
        axis.text.y = element_blank(),
        panel.grid = element_blank(),
        legend.position = "bottom") +
  labs(x = "", y = "day of week", color = "seal-hours",
       size = "seal hours of bio-logger data") +
  ggtitle("Haul-out behavior data is concentrated in the months of May and June",
          subtitle = "data presented in seal-hours collated across years (2005-2020)")
```
